%-------------------------
% Jake's Resume Style — Oğuz Gençer
% Clean, minimal, maximum ATS compatibility
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{geometry}

\geometry{top=0.5in, bottom=0.5in, left=0.55in, right=0.55in}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%--- Custom commands ---
\newcommand{\resumeItem}[1]{
  \item\small{#1\vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingThree}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small#2} \\
      \textit{\small#3} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumePub}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & \textit{\small#2} \\
      \small\textit{#3} \\
      \small\href{#4}{\texttt{\small#4}} \\
    \end{tabular*}\vspace{-4pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-2pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%======================================================
\begin{document}

%----- HEADER -----
\begin{center}
  {\Huge \scshape O\u{g}uz Gen\c{c}er} \\[4pt]
  \small
  Istanbul, Turkey \,$|$\,
  \href{mailto:oguzgencer@gmail.com}{oguzgencer@gmail.com} \,$|$\,
  \href{https://linkedin.com/in/oguzgencer}{linkedin.com/in/oguzgencer} \,$|$\,
  \href{https://github.com/drader}{github.com/drader} \,$|$\,
  \href{https://oguzgencer.dev}{oguzgencer.dev}
\end{center}

%----- SUMMARY -----
\section{Summary}
\small{
PhD researcher and software engineer bridging nanoscience and AI. Research focus: neuromorphic computing and biocompatible nanosensors for neural signal recording at the neuron-electrode interface. Industry experience in GenAI systems, embedded firmware, and CI/CD pipelines -- spanning consumer electronics to Fortune~500 enterprise R\&D. 3 peer-reviewed publications across journal and conference venues. Open-source builder: memex ecosystem (papervault, docvault, podvault).
}
\vspace{-4pt}

%----- TECHNICAL SKILLS -----
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Nanoscience:} Quantum Dot Synthesis, Nanosensor Fabrication, SEM, TEM, AFM, Raman, XPS, FTIR, Nanoelectronics, Device Modeling, TCAD, Photolithography, E-Beam Lithography \\[2pt]
    \textbf{Embedded Systems:} C, C++, Java, VHDL, FPGA, Matlab/Simulink, Altium, KiCad, LTSpice \\[2pt]
    \textbf{AI \& Data Science:} Python, TensorFlow/Keras, PyTorch, LangChain, LangFlow, Intel Loihi 2 (SNN), pandas, NumPy, TypeScript/Node.js, ParaView, VTK, HDF5 \\[2pt]
    \textbf{DevOps:} Git/GitHub, Docker, Jenkins, CI/CD Pipelines, SQL, Linux/Shell \\[2pt]
    \textbf{Management:} Scrum Master (PSM1), Agile/Jira, Team Leadership, Stakeholder Management
  }}
\end{itemize}

%----- EXPERIENCE -----
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Istanbul Technical University}{Sep 2022 -- Present}
    {PhD Researcher}{Istanbul, Turkey}
    \resumeItemListStart
      \resumeItem{Developing a novel noninvasive nanosensor for neural activity recording; fabricating biocompatible nanofiber-based coatings at the neuron-electrode interface to improve signal quality in primary neuron cultures.}
      \resumeItem{Specializing in neuromorphic computing, nanoelectronics, AI/data science, and TCAD device simulation.}
    \resumeItemListEnd

  \resumeSubheading
    {BSH Turkey -- Bosch-Siemens Home Appliances}{May 2022 -- May 2025}
    {Software Engineer, R\&D -- Cooling Division}{Tekirda\u{g}, Turkey}
    \resumeItemListStart
      \resumeItem{Formally assigned to a Bavaria Government-funded project with BSH Germany; developed a GenAI system (LangChain) to automate requirement document generation.}
      \resumeItem{Pioneered an AI Core Team initiative: organized brainstorming sessions, drafted a year-long training curriculum, and prepared AI project proposals.}
      \resumeItem{Managed CI/CD pipelines and Agile release deliveries; implemented ambient light feature for embedded firmware.}
    \resumeItemListEnd

  \resumeSubheading
    {Istanbul Technical University -- BeeDot Research Group}{Sep 2019 -- Jun 2021}
    {MSc Researcher}{Istanbul, Turkey}
    \resumeItemListStart
      \resumeItem{Synthesized Zinc-Doped Carbon-Based Quantum Dots via microwave-assisted methods.}
      \resumeItem{Characterized samples using UV-VIS, FTIR, XPS, SEM, and TEM; findings published in \textit{Diamond and Related Materials} (2022).}
    \resumeItemListEnd

  \resumeSubheading
    {Sunny Electronics}{Jul 2020 -- Jan 2021}
    {Software Engineer, R\&D}{Istanbul, Turkey}
    \resumeItemListStart
      \resumeItem{Developed a WiFi remote control application for Bluetoothless Android TVs.}
      \resumeItem{Managed configuration, release, and CI/CD process for Android TV software.}
    \resumeItemListEnd

  \resumeSubheading
    {Rigel Technology}{Oct 2019 -- Mar 2020}
    {Software Engineer, R\&D}{Istanbul, Turkey}
    \resumeItemListStart
      \resumeItem{Developed Windows device driver software for VR motion control devices.}
      \resumeItem{Built a control interface for device testing and hardware validation.}
    \resumeItemListEnd

  \resumeSubheading
    {Istanbul Technical University -- ECC Lab}{Jul 2018 -- Mar 2019}
    {MSc Researcher}{Istanbul, Turkey}
    \resumeItemListStart
      \resumeItem{Contributed to design and verification of a novel nanodevice using TCAD and LTSpice simulation.}
      \resumeItem{Implemented genetic algorithms for device parameter optimization; published at DATE 2019 conference.}
    \resumeItemListEnd

  \resumeSubheading
    {Labirent Building Automation}{Feb 2018 -- Jul 2018}
    {System Engineer \& Team Lead}{Istanbul, Turkey}
    \resumeItemListStart
      \resumeItem{Designed and commissioned building automation projects (AV systems, meeting rooms, TV walls, security) as turn-key solutions.}
      \resumeItem{Led a team of 8 technicians; coordinated between company, clients, and contractors.}
    \resumeItemListEnd

  \resumeSubheading
    {FOTECH}{Aug 2016 -- Aug 2017}
    {Project Engineer \& Team Lead}{Istanbul, Turkey / Kabul, Afghanistan}
    \resumeItemListStart
      \resumeItem{Managed a team of 12 to complete fiber-optic network, telecom, and security camera infrastructure for the U.S. Embassy facility in Kabul.}
      \resumeItem{Coordinated between government authorities and contracting companies in a high-stakes field environment.}
    \resumeItemListEnd

  \resumeSubheading
    {Dehenken Limited -- AIESEC Internship}{Sep 2012 -- Feb 2013}
    {Junior Developer}{Kyoto, Japan}
    \resumeItemListStart
      \resumeItem{Developed a demo application for the IoT/Android-based Derimo project.}
      \resumeItem{Contributed to PIDP (Personal Identity Detection Project) using Turkish language specifications.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----- EDUCATION -----
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {Istanbul Technical University}{Sep 2022 -- Present}
    {PhD in Nanoscience \& Nanoengineering}{Istanbul, Turkey}
    \resumeItemListStart
      \resumeItem{\textit{Thesis:} Fabrication and characterization of a biocompatible nanofiber-based coating for the neuron-electrode interface to improve signal quality in primary neuron cultures.}
    \resumeItemListEnd

  \resumeSubheading
    {Istanbul Technical University}{Feb 2018 -- Jun 2021}
    {M.Sc. in Nanoscience \& Nanoengineering}{Istanbul, Turkey}
    \resumeItemListStart
      \resumeItem{\textit{Thesis:} Zinc-Doped Carbon-Based Quantum Dot Synthesis \& Characterization.}
    \resumeItemListEnd

  \resumeSubheading
    {Istanbul Aydin University}{Feb 2013 -- Feb 2015}
    {B.Sc. in Electrical \& Electronics Engineering}{Istanbul, Turkey}
    \resumeItemListStart
      \resumeItem{\textit{Graduation Project:} Modeling and simulation of the ABB IRB120 6-DOF industrial robot arm using Matlab \& Simulink.}
    \resumeItemListEnd

  \resumeSubheading
    {Eskisehir Osmangazi University}{Sep 2008 -- Jul 2012}
    {B.Sc. in Electrical \& Electronics Engineering}{Eskisehir, Turkey}
    \resumeItemListStart
      \resumeItem{Founded HIDROGU -- a hydrogen-powered vehicle research team exploring renewable energy systems.}
    \resumeItemListEnd

  \resumeSubheading
    {Istanbul University -- Vocational School of Technical Sciences}{Sep 2005 -- Jul 2007}
    {Associate Degree in Biomedical Device Technology}{Istanbul, Turkey}

\resumeSubHeadingListEnd

%----- PUBLICATIONS -----
\section{Publications}
\resumeSubHeadingListStart

  \item\small{
    O. Gen\c{c}er et al., ``Triggering excitation independent fluorescence in zinc(II) incorporated carbon dots: Surface passivation of carbon dots with zinc(II) ions by microwave assisted synthesis methods,''
    \textit{Diamond and Related Materials}, Vol. 123, 2022. \href{https://doi.org/10.1016/j.diamond.2022.108874}{doi:10.1016/j.diamond.2022.108874}
  }\vspace{-2pt}

  \item\small{
    S. Safaltin et al. (incl. O. Gen\c{c}er), ``Realization of four-terminal switching lattices: Technology development and circuit modeling,''
    \textit{Design, Automation \& Test in Europe (DATE 2019)}, 2019. \href{https://doi.org/10.23919/DATE.2019.8715123}{doi:10.23919/DATE.2019.8715123}
  }\vspace{-2pt}

  \item\small{
    O. Gen\c{c}er, ``Zinc Doped Carbon Based Quantum Dot Synthesis \& Characterization'' (MSc Thesis),
    Istanbul Technical University, 2021. \href{https://doi.org/10.13140/RG.2.2.19652.91526}{doi:10.13140/RG.2.2.19652.91526}
  }

\resumeSubHeadingListEnd

%----- SELECTED PROJECTS -----
\section{Selected Projects}
\resumeSubHeadingListStart

  \resumeSubheading
    {memex -- Agentic Wiki Template}{Released}
    {TypeScript, Claude API, MCP, obsidian-hybrid-search}{\href{https://github.com/drader/memex}{github.com/drader/memex}}
    \resumeItemListStart
      \resumeItem{Hybrid agentic wiki foundation with BM25 + vector search (RRF). Spawned three specialized tools: papervault (arXiv research), docvault (developer docs), podvault (podcast transcripts).}
    \resumeItemListEnd

  \resumeSubheading
    {NeuralLab Assistant}{In Development}
    {Python, Voice UI, Protocol Tracking}{}
    \resumeItemListStart
      \resumeItem{Hands-free voice assistant for primary neuron culture labs -- handles note-taking, timers, calculations, and protocol step tracking to eliminate contamination risk from device contact.}
    \resumeItemListEnd

  \resumeSubheading
    {ABB IRB120 Robot Arm Simulation}{Completed, 2014}
    {Matlab, Simulink, SimMechanics}{\href{https://github.com/drader/project-irb120}{github.com/drader/project-irb120}}
    \resumeItemListStart
      \resumeItem{Full mathematical model and dynamic simulation of the 6-DOF ABB IRB120 industrial robot arm: DH parameters, Lagrangian dynamics, quintic trajectory generation, and PID joint control.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----- CERTIFICATIONS -----
\section{Certifications}
\resumeSubHeadingListStart
  \resumeSubheading{Professional Scrum Master (PSM1)}{Jun 2023}{Scrum.org}{}
  \resumeSubheading{Advanced Hardware Design with Altium}{Jan 2022}{Fedevel Academy}{}
\resumeSubHeadingListEnd

\end{document}
