%-------------------------
% moderncv — Banking Style — Oğuz Gençer
% ATS score: 9/10 | Clean horizontal layout
%-------------------------
\documentclass[10.5pt, letterpaper]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[scale=0.90, top=1.2cm, bottom=1.2cm]{geometry}

% Experience entry: Company -- Title (left bold) | Location -- Date (right italic)
% #1=company-title, #2=location, #3=date, #4=description
\newcommand{\cvexp}[4]{%
  \vspace{3pt}\par\noindent
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \small\textit{#2 \textendash\ #3}\\
  \end{tabular*}\vspace{-4pt}
  #4\vspace{1pt}%
}

% Custom project entry: name+link (left bold) | status (right bold)
% #1=full left content (name + optional link), #2=status, #3=description
\newcommand{\cvproject}[3]{%
  \vspace{3pt}%
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}%
    \textbf{#1} & \textbf{#2}\\%
  \end{tabular*}\\[-3pt]%
  \small #3\par\vspace{1pt}%
}

% Personal info
\name{O\u{g}uz}{Gen\c{c}er}
\title{Electronics \& AI Engineer $|$ Nanoscience PhD Candidate}
\address{Istanbul, Turkey}{}{}
\email{oguzgencer@gmail.com}
\homepage{drader.github.io/portfolio}
\social[linkedin]{oguzgencer}
\social[github]{drader}
\extrainfo{ORCID: 0000-0001-7460-9984}

%======================================================
\begin{document}

\makecvtitle
\vspace{-18pt}

%----- SUMMARY -----
\section{Summary}
Electrical \& Electronics Engineer and Nanoscience PhD Candidate working at the intersection of nanoelectronics and AI. Research focus: biocompatible nanosensors for neural signal recording and the hardware foundations that neuromorphic computing systems require. AI expertise spans two tracks: neuromorphic systems (Intel Loihi~2, SNNs) as the long-term research direction, and applied GenAI (LangChain, LLMs) from Fortune~500 industry experience. Software background is hardware-adjacent throughout -- embedded firmware, device drivers, IoT, and industrial automation. 3 peer-reviewed publications. Open-source builder: memex ecosystem (papervault, docvault, podvault). Worked in Turkey, Japan, and Afghanistan.

%----- TECHNICAL SKILLS -----
\section{Technical Skills}
\cvitem{Nanoscience}{Quantum Dot Synthesis, Nanosensor Fabrication, SEM, TEM, AFM, Raman, XPS, FTIR, Nanoelectronics, TCAD, LTSpice, Photolithography, E-Beam Lithography}
\cvitem{Electronics \& Embedded}{C, C++, VHDL, FPGA, Matlab/Simulink, Altium, KiCad, Firmware Development, Device Drivers}
\cvitem{AI \& Data Science}{Python, TensorFlow/Keras, PyTorch, LangChain, LangFlow, Intel Loihi~2 (SNN), pandas, NumPy, TypeScript/Node.js, ParaView, VTK, HDF5}
\cvitem{DevOps}{Git/GitHub, Docker, Jenkins, CI/CD Pipelines, SQL, Linux/Shell}
\cvitem{Management}{Scrum Master (PSM1), Agile/Jira, Team Leadership, Stakeholder Management}

%----- EXPERIENCE -----
\section{Experience}

\cvexp{Istanbul Technical University -- PhD Candidate}{Istanbul, Turkey}{Sep 2022 -- Present}{
  \begin{itemize}
    \item Developing a novel noninvasive nanosensor for neural activity recording; fabricating biocompatible nanofiber-based coatings at the neuron-electrode interface to improve signal quality in primary neuron cultures.
    \item Specializing in neuromorphic computing, nanoelectronics, and AI/data science; using Intel Loihi~2 for SNN experiments and TCAD for device simulation.
  \end{itemize}
}

\cvexp{BSH Turkey (Bosch-Siemens Home Appliances) -- Software Engineer, R\&D}{Tekirda\u{g}, Turkey}{May 2022 -- May 2025}{
  \begin{itemize}
    \item Formally assigned to a Bavaria Government-funded LLM project with BSH Germany; developed a GenAI system (LangChain) to automate requirement document generation.
    \item Pioneered an AI Core Team initiative: organized brainstorming sessions, drafted a year-long training curriculum, and prepared AI project proposals for the local R\&D team.
    \item Managed CI/CD pipelines and Agile release deliveries; implemented ambient light feature for embedded firmware.
  \end{itemize}
}

\cvexp{Sunny Electronics -- Software Engineer, R\&D}{Istanbul, Turkey}{Jul 2020 -- Jan 2021}{
  \begin{itemize}
    \item Developed WiFi remote control software for Android TV platforms; managed release and CI/CD pipeline.
  \end{itemize}
}

\cvexp{Rigel Technology -- Software Engineer, R\&D}{Istanbul, Turkey}{Oct 2019 -- Mar 2020}{
  \begin{itemize}
    \item Developed Windows device driver software for VR motion control devices; built a hardware control and testing interface.
  \end{itemize}
}

\cvexp{Istanbul Technical University, BeeDot Research Group -- MSc Researcher}{Istanbul, Turkey}{Sep 2019 -- Jun 2021}{
  \begin{itemize}
    \item Synthesized Zinc-Doped Carbon-Based Quantum Dots via microwave-assisted methods.
    \item Characterized using UV-VIS, FTIR, XPS, SEM, and TEM; published in \textit{Diamond and Related Materials} (2022).
  \end{itemize}
}

\cvexp{Istanbul Technical University, ECC Lab -- MSc Researcher}{Istanbul, Turkey}{Jul 2018 -- Mar 2019}{
  \begin{itemize}
    \item Contributed to design and verification of a novel nanodevice using TCAD and LTSpice; implemented genetic algorithms for parameter optimization. Published at DATE 2019.
  \end{itemize}
}

\cvexp{Labirent Building Automation -- System Engineer \& Team Lead}{Istanbul, Turkey}{Feb 2018 -- Jul 2018}{
  \begin{itemize}
    \item Designed and commissioned turn-key building automation projects (AV, security, meeting rooms); led a team of 8 technicians.
  \end{itemize}
}

\cvexp{FOTECH -- Project Engineer \& Team Lead}{Istanbul, Turkey / Kabul, Afghanistan}{Aug 2016 -- Aug 2017}{
  \begin{itemize}
    \item Led 12-person team delivering fiber-optic, telecom, and security camera infrastructure for the U.S. Embassy in Kabul; coordinated with government authorities and contractors.
  \end{itemize}
}

\cvexp{Dehenken Limited, AIESEC Internship -- Junior Developer}{Kyoto, Japan}{Sep 2012 -- Feb 2013}{
  \begin{itemize}
    \item Developed IoT/Android demo app (Derimo project); contributed to a Personal Identity Detection system.
  \end{itemize}
}

%----- EDUCATION -----
\section{Education}

\cventry{Sep 2022 -- Present}{PhD in Nanoscience \& Nanoengineering}{Istanbul Technical University}{Istanbul, Turkey}{}{
  \textit{Thesis:} Fabrication and characterization of a biocompatible nanofiber-based coating for the neuron-electrode interface to improve signal quality in primary neuron cultures.
}

\cventry{Feb 2018 -- Jun 2021}{M.Sc. in Nanoscience \& Nanoengineering}{Istanbul Technical University}{Istanbul, Turkey}{}{
  \textit{Thesis:} Zinc-Doped Carbon-Based Quantum Dot Synthesis \& Characterization.
}

\cventry{Feb 2013 -- Feb 2015}{B.Sc. in Electrical \& Electronics Engineering}{Istanbul Aydin University}{Istanbul, Turkey}{}{
  \textit{Graduation Project:} Modeling and simulation of the ABB IRB120 6-DOF industrial robot arm using Matlab \& Simulink.
}

\cventry{Sep 2008 -- Jul 2012}{B.Sc. in Electrical \& Electronics Engineering}{Eskisehir Osmangazi University}{Eskisehir, Turkey}{}{
  Founded HIDROGU -- a hydrogen-powered vehicle research team exploring renewable energy systems.
}

\cventry{Sep 2005 -- Jul 2007}{Associate Degree in Biomedical Device Technology}{Istanbul University -- Vocational School of Technical Sciences}{Istanbul, Turkey}{}{}

%----- PUBLICATIONS -----
\section{Publications}

\cvitem{2022}{O. Gen\c{c}er et al., ``Triggering excitation independent fluorescence in zinc(II) incorporated carbon dots,'' \textit{Diamond Relat. Mater.}, 123. \href{https://doi.org/10.1016/j.diamond.2022.108874}{doi:10.1016/j.diamond.2022.108874}}

\cvitem{2021}{O. Gen\c{c}er, ``Zinc Doped Carbon Based Quantum Dot Synthesis \& Characterization'' (MSc Thesis), ITU. \href{https://doi.org/10.13140/RG.2.2.19652.91526}{doi:10.13140/RG.2.2.19652.91526}}

\cvitem{2019}{S. Safaltin et al. (incl. O. Gen\c{c}er), ``Realization of four-terminal switching lattices: Technology development and circuit modeling,'' \textit{DATE 2019}. \href{https://doi.org/10.23919/DATE.2019.8715123}{doi:10.23919/DATE.2019.8715123}}

%----- SELECTED PROJECTS -----
\section{Selected Projects}

\cvproject{memex -- Agentic Wiki Template -- \href{https://github.com/drader/memex}{github.com/drader/memex}}{Released}{Hybrid agentic wiki foundation with BM25 + vector search (RRF). TypeScript, Claude API, MCP. Foundation for papervault (arXiv), docvault (developer docs), and podvault (podcasts).}

\cvproject{NeuralLab Assistant}{In Development}{Hands-free voice assistant for neuron culture labs -- eliminates contamination risk by handling note-taking, timers, calculations, and protocol tracking through voice commands only.}

\cvproject{ABB IRB120 Robot Arm Simulation -- \href{https://github.com/drader/project-irb120}{github.com/drader/project-irb120}}{Completed 2014}{Full 6-DOF dynamic simulation: DH parameters, Lagrangian dynamics, quintic trajectory generation, PID joint control. Geometry from official ABB CAD files.}

%----- CERTIFICATIONS -----
\section{Certifications}
\cvlistitem{PSM1 Scrum Master -- Scrum.org (Jun 2023)}
\cvlistitem{Advanced Hardware Design with Altium -- Fedevel Academy (Jan 2022)}

\end{document}
