%-------------------------
% Visual/Modern Style — Oğuz Gençer
% Awesome-CV inspired aesthetics, ATS-safe single-column implementation
%-------------------------
\documentclass[letterpaper,10.5pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{microtype}

\geometry{top=0.45in, bottom=0.45in, left=0.6in, right=0.6in}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Accent color
\definecolor{accent}{HTML}{1B4F8A}   % deep navy blue

% Section formatting — colored title + thick rule
\titleformat{\section}{
  \vspace{2pt}\color{accent}\large\bfseries\raggedright
}{}{0em}{}[{\color{accent}\titlerule[1.2pt]}\vspace{-5pt}]

%--- Custom commands ---
\newcommand{\myname}[1]{{\Huge\bfseries #1}}
\newcommand{\myrole}[1]{{\large\color{accent} #1}}

\newcommand{\resumeItem}[1]{
  \item\small{#1\vspace{-1pt}}
}

\newcommand{\entryHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small\textit{\color{gray}#2} \\
      \small\textit{\color{accent!80}#3} & \small\textit{\color{gray}#4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\entryHeadingTwo}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small\textit{\color{gray}#2} \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\small$\circ$}}$}

\newcommand{\listStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\listEnd}{\end{itemize}}
\newcommand{\bulletStart}{\begin{itemize}[leftmargin=0.2in]\vspace{-2pt}}
\newcommand{\bulletEnd}{\end{itemize}\vspace{-5pt}}

%======================================================
\begin{document}

%----- HEADER -----
\begin{center}
  \myname{O\u{g}uz Gen\c{c}er} \\[5pt]
  \myrole{PhD Researcher \& Software Engineer} \\[6pt]
  \small
  \textcolor{gray}{Istanbul, Turkey}
  \;\textbf{\textcolor{accent}{·}}\;
  \href{mailto:oguzgencer@gmail.com}{\textcolor{gray}{oguzgencer@gmail.com}}
  \;\textbf{\textcolor{accent}{·}}\;
  \href{https://linkedin.com/in/oguzgencer}{\textcolor{gray}{linkedin.com/in/oguzgencer}}
  \;\textbf{\textcolor{accent}{·}}\;
  \href{https://github.com/drader}{\textcolor{gray}{github.com/drader}}
  \;\textbf{\textcolor{accent}{·}}\;
  \href{https://oguzgencer.dev}{\textcolor{gray}{oguzgencer.dev}}
  \\[3pt]
  \href{https://orcid.org/0000-0001-7460-9984}{\textcolor{gray}{ORCID: 0000-0001-7460-9984}}
\end{center}

\vspace{2pt}
{\color{accent!30}\hrule height 0.5pt}
\vspace{6pt}

%----- SUMMARY -----
\section{Summary}
\small{
PhD researcher and software engineer bridging nanoscience and AI. Research focus: neuromorphic computing and biocompatible nanosensors for neural signal recording at the neuron-electrode interface. Industry background spans GenAI systems (LangChain, LLMs), embedded firmware, and CI/CD pipelines -- from consumer electronics to Fortune~500 enterprise R\&D. 3 peer-reviewed publications. Open-source builder: the memex ecosystem (papervault, docvault, podvault). Worked in Turkey, Japan, and Afghanistan.
}
\vspace{-2pt}

%----- TECHNICAL SKILLS -----
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{\textcolor{accent}{Nanoscience:}} Quantum Dot Synthesis, Nanosensor Fabrication, SEM, TEM, AFM, Raman, XPS, FTIR, Nanoelectronics, TCAD, LTSpice, Photolithography, E-Beam Lithography \\[2pt]
    \textbf{\textcolor{accent}{Embedded Systems:}} C, C++, Java, VHDL, FPGA, Matlab/Simulink, Altium, KiCad \\[2pt]
    \textbf{\textcolor{accent}{AI \& Data Science:}} Python, TensorFlow/Keras, PyTorch, LangChain, LangFlow, Intel Loihi~2 (SNN), pandas, NumPy, TypeScript/Node.js, ParaView, VTK, HDF5 \\[2pt]
    \textbf{\textcolor{accent}{DevOps:}} Git/GitHub, Docker, Jenkins, CI/CD Pipelines, SQL, Linux/Shell \\[2pt]
    \textbf{\textcolor{accent}{Management:}} Scrum Master (PSM1), Agile/Jira, Team Leadership, Stakeholder Management
  }}
\end{itemize}

%----- EXPERIENCE -----
\section{Experience}
\listStart

  \entryHeading
    {Istanbul Technical University}{Sep 2022 -- Present}
    {PhD Researcher}{Istanbul, Turkey}
    \bulletStart
      \resumeItem{Developing a novel noninvasive nanosensor for neural activity recording; fabricating biocompatible nanofiber-based coatings at the neuron-electrode interface to improve signal quality in primary neuron cultures.}
      \resumeItem{Specializing in neuromorphic computing, nanoelectronics, AI/data science, and TCAD device simulation. Using Intel Loihi~2 for SNN experiments.}
    \bulletEnd

  \entryHeading
    {BSH Turkey -- Bosch-Siemens Home Appliances}{May 2022 -- May 2025}
    {Software Engineer, R\&D -- Cooling Division}{Tekirda\u{g}, Turkey}
    \bulletStart
      \resumeItem{Formally assigned to a Bavaria Government-funded LLM project with BSH Germany; developed a GenAI system (LangChain) to automate requirement document generation.}
      \resumeItem{Pioneered an AI Core Team initiative: organized brainstorming sessions, drafted a year-long training curriculum, and prepared AI project proposals for the local R\&D team.}
      \resumeItem{Managed CI/CD pipelines and Agile release deliveries; implemented ambient light feature for embedded firmware.}
    \bulletEnd

  \entryHeading
    {Istanbul Technical University -- BeeDot Research Group}{Sep 2019 -- Jun 2021}
    {MSc Researcher}{Istanbul, Turkey}
    \bulletStart
      \resumeItem{Synthesized Zinc-Doped Carbon-Based Quantum Dots via microwave-assisted methods.}
      \resumeItem{Characterized samples using UV-VIS, FTIR, XPS, SEM, and TEM; findings published in \textit{Diamond and Related Materials} (2022).}
    \bulletEnd

  \entryHeading
    {Sunny Electronics}{Jul 2020 -- Jan 2021}
    {Software Engineer, R\&D}{Istanbul, Turkey}
    \bulletStart
      \resumeItem{Developed a WiFi remote control application for Bluetoothless Android TVs; managed CI/CD and release process.}
    \bulletEnd

  \entryHeading
    {Rigel Technology}{Oct 2019 -- Mar 2020}
    {Software Engineer, R\&D}{Istanbul, Turkey}
    \bulletStart
      \resumeItem{Developed Windows device driver software for VR motion control devices; built a hardware control and testing interface.}
    \bulletEnd

  \entryHeading
    {Istanbul Technical University -- ECC Lab}{Jul 2018 -- Mar 2019}
    {MSc Researcher}{Istanbul, Turkey}
    \bulletStart
      \resumeItem{Contributed to design and verification of a novel nanodevice using TCAD and LTSpice; implemented genetic algorithms for parameter optimization. Published at DATE 2019.}
    \bulletEnd

  \entryHeading
    {Labirent Building Automation}{Feb 2018 -- Jul 2018}
    {System Engineer \& Team Lead}{Istanbul, Turkey}
    \bulletStart
      \resumeItem{Designed and commissioned building automation projects as turn-key solutions; led a team of 8 technicians.}
    \bulletEnd

  \entryHeading
    {FOTECH}{Aug 2016 -- Aug 2017}
    {Project Engineer \& Team Lead}{Istanbul, Turkey / Kabul, Afghanistan}
    \bulletStart
      \resumeItem{Led a team of 12 to complete fiber-optic network, telecom, and security camera infrastructure for the U.S. Embassy facility in Kabul.}
    \bulletEnd

  \entryHeading
    {Dehenken Limited -- AIESEC Internship}{Sep 2012 -- Feb 2013}
    {Junior Developer}{Kyoto, Japan}
    \bulletStart
      \resumeItem{Developed a demo app for the IoT/Android-based Derimo project; contributed to a Personal Identity Detection system.}
    \bulletEnd

\listEnd

%----- EDUCATION -----
\section{Education}
\listStart

  \entryHeading
    {Istanbul Technical University}{Sep 2022 -- Present}
    {PhD in Nanoscience \& Nanoengineering}{Istanbul, Turkey}
    \bulletStart
      \resumeItem{\textit{Thesis:} Fabrication and characterization of a biocompatible nanofiber-based coating for the neuron-electrode interface to improve signal quality in primary neuron cultures.}
    \bulletEnd

  \entryHeading
    {Istanbul Technical University}{Feb 2018 -- Jun 2021}
    {M.Sc. in Nanoscience \& Nanoengineering}{Istanbul, Turkey}
    \bulletStart
      \resumeItem{\textit{Thesis:} Zinc-Doped Carbon-Based Quantum Dot Synthesis \& Characterization.}
    \bulletEnd

  \entryHeading
    {Istanbul Aydin University}{Feb 2013 -- Feb 2015}
    {B.Sc. in Electrical \& Electronics Engineering}{Istanbul, Turkey}
    \bulletStart
      \resumeItem{\textit{Graduation Project:} Modeling and simulation of the ABB IRB120 6-DOF industrial robot arm using Matlab \& Simulink.}
    \bulletEnd

  \entryHeading
    {Eskisehir Osmangazi University}{Sep 2008 -- Jul 2012}
    {B.Sc. in Electrical \& Electronics Engineering}{Eskisehir, Turkey}
    \bulletStart
      \resumeItem{Founded HIDROGU -- a hydrogen-powered vehicle research team exploring renewable energy systems.}
    \bulletEnd

  \entryHeadingTwo
    {Istanbul University -- Vocational School of Technical Sciences}{Sep 2005 -- Jul 2007}

\listEnd

%----- PUBLICATIONS -----
\section{Publications}
\listStart

  \item\small{
    O. Gen\c{c}er et al., ``Triggering excitation independent fluorescence in zinc(II) incorporated carbon dots,''
    \textit{Diamond and Related Materials}, Vol.~123, 2022.
    \textcolor{accent}{\href{https://doi.org/10.1016/j.diamond.2022.108874}{doi:10.1016/j.diamond.2022.108874}}
  }\vspace{2pt}

  \item\small{
    S. Safaltin et al. (incl. O. Gen\c{c}er), ``Realization of four-terminal switching lattices: Technology development and circuit modeling,''
    \textit{DATE 2019 Conference}, 2019.
    \textcolor{accent}{\href{https://doi.org/10.23919/DATE.2019.8715123}{doi:10.23919/DATE.2019.8715123}}
  }\vspace{2pt}

  \item\small{
    O. Gen\c{c}er, ``Zinc Doped Carbon Based Quantum Dot Synthesis \& Characterization'' (MSc Thesis),
    Istanbul Technical University, 2021.
    \textcolor{accent}{\href{https://doi.org/10.13140/RG.2.2.19652.91526}{doi:10.13140/RG.2.2.19652.91526}}
  }

\listEnd

%----- SELECTED PROJECTS -----
\section{Selected Projects}
\listStart

  \entryHeading
    {memex -- Agentic Wiki Template}{Released}
    {TypeScript, Claude API, MCP, obsidian-hybrid-search}{\href{https://github.com/drader/memex}{github.com/drader/memex}}
    \bulletStart
      \resumeItem{Hybrid agentic wiki foundation with BM25 + vector search (RRF). Foundation for papervault (arXiv research), docvault (developer docs), and podvault (podcast transcripts).}
    \bulletEnd

  \entryHeading
    {NeuralLab Assistant}{In Development}
    {Python, Voice UI, Protocol Tracking}{}
    \bulletStart
      \resumeItem{Hands-free voice assistant for neuron culture labs -- eliminates contamination risk by handling note-taking, timers, calculations, and protocol tracking through voice commands only.}
    \bulletEnd

  \entryHeading
    {ABB IRB120 Robot Arm Simulation}{Completed, 2014}
    {Matlab, Simulink, SimMechanics}{\href{https://github.com/drader/project-irb120}{github.com/drader/project-irb120}}
    \bulletStart
      \resumeItem{Full 6-DOF dynamic simulation: DH parameters, Lagrangian dynamics, quintic trajectory generation, PID joint control. Geometry imported from official ABB CAD files.}
    \bulletEnd

\listEnd

%----- CERTIFICATIONS -----
\section{Certifications}
\listStart
  \entryHeadingTwo{Professional Scrum Master (PSM1) -- Scrum.org}{Jun 2023}
  \entryHeadingTwo{Advanced Hardware Design with Altium -- Fedevel Academy}{Jan 2022}
\listEnd

\end{document}
